%!TEX TS-program = xelatex
\documentclass[a4paper,online]{adcv}

\newcommand*{\hib}{Sacred Heart University, Fairfield, CT}

\title{Michael Bazos’s CV}

\adcvname{Michael}{Bazos}{}
\adcvtitle{Software Engineer}
\adcvaddress{135 Far Horizon Drive}{06612}{Easton}{CT}
\adcvwebsite{https://github.com/mbazos}{https://github.com/mbazos}
\adcvemail{mbbazos}{gmail}{com}
\adcvphone{(413) 695 6074}
\adcvdate{April 2021}
\begin{document}

I’m a highly motivated software engineer with a breath of technical experience, seeking a position in a fast-paced team environment where I can utilize the full range of my skills, which include a concentration in Java, design patterns and specialized skills related to web services, message brokers and business to business integration.

\section{Summary of Qualifications}

\begin{adcvtabletwo}
Software Engineer with 15 years of experience, a Bachelors of Science degree in Computer Science and a Minor in Mathematics.
  \begin{itemize}
    \item Proven ability to analyze complicated problems and design and implement solutions that meet ever changing business requirements
    \item Adaptable to learn new technologies and patterns
    \item Expertise in Java with professional experience with JavaScript (ES6+), Node.js, Typescript \& Python
    \item Passionate about API's, system integration, web services and implementing robust solutions
    \item Excellent communication skills, good team player and actively mentor other engineers
    \item Proven documentation skills such as writing design documentation, charting and writing technical documents for other engineers
    \item Experience with managing shared components/libraries used by other engineers across the organization
    \item Advocate and lead the JVM dev group at Priceline collaborating with various teams using JVM technologies at Priceline
  \end{itemize}
\end{adcvtabletwo}

\section{Experience}

\begin{adcvtabletwo}
  {\textbf{Priceline.com}, Norwalk, CT}
  
  \adcvrowtwo{\textbf{Distinguished Engineer}, Rental Car Services} {Mar 2018-Present}
  \adcvrowskip
  \adcvrowmulti{Stepped into this role to help lead the company efforts to move application workloads into the cloud and off of Priceline's on-prem data centers. Worked with a small team of people to develop the patterns for Priceline and personally spent time on all aspects of the cloud migration. Beyond developing the strategy and patterns I worked on Priceline's infra libraries (Java) to enable the backend teams to take legacy applications to the cloud with minimal changes. I was also responsible to train and meet with every development/product team at Priceline to walk them through how they can migrate their applications and what to expect on the new platform. This included 15+ teams. Beyond applications I was also heavily involved in various strategies around how teams can manage moving data to the cloud. In addition to the cloud infrastructure/application responsibilities I also working with my core rental car team on product/business initiatives and applied the patterns, concepts and strategy to my own teams applications that we owned to validate our documentation and patterns. I continue to help and enable the engineers at Priceline in their cloud journey by being actively involved helping teams throughout the organization. }
  \textbf{Relevant Technologies} Helm Charts, Docker, Kubernetes, Java, Node.js, Kafka, Oracle DB, MySql, Redis, Cassandra, Google Cloud Platform

  \adcvrowskip
  {\textbf{Priceline.com}, Norwalk, CT}
  
  \adcvrowtwo{\textbf{Principal Engineer}, Rental Car Services Team} {Mar 2016-2018}
  \adcvrowmulti{Leadership role on the rental car team as an individual contributor and designed and worked towards our rental car team long term business, product and technology goals. Some of the highlights include consolidating redundant API's, onboarding new supplier systems, onboarding new affiliates, internationalizing the rental car path and working closely with our front end team to help them migrate from a legacy front end to a more modern front end using Node.js + AnuglarJS.}
  \textbf{Relevant Technologies} REST, JSON, Java, Spring Framework, Spring Boot, Tomcat, Oracle DB, MySql DB, Cassandra, Lucene, XML, Node.js, AnuglarJS
  
  \adcvrowskip
  {\textbf{Priceline.com}, Norwalk, CT}
  
  \adcvrowtwo{\textbf{Senior Software Engineer}, Rental Car Services Team} {Apr 2013-2016}
  \adcvrowmulti{Joined the rental car services team as an individual contributor heads down in building out new features, learning the rental car business and looking for opportunities to improve our systems and grow the business. We had a small but dynamic team and focused on projects that would have direct growth to our business. Some of the highlights during this time included adding new products for rental cars, removing our legacy EJB infrastructure, improving our unit tests/CI tools and implementing a specialized DB caching resulting +25\% reduction in page load speeds. During this time the rental car team and my direct contributions were able to help the business achieve quarter after quarter growth of +20\% in growth of the rental car product}
  \textbf{Relevant Technologies} REST, JSON, Java, Spring Framework, Spring Boot, Tomcat, Oracle DB, MySql DB, Cassandra, Lucene, XML
  
  \adcvrowskip
  {\textbf{Cigna}, Bloomfield, CT}
  
  \adcvrowtwo{\textbf{Senior Application Developer}, SEI} {Feb 2011-2013}
  \adcvrowmulti{Designed and implemented Java enterprise components at Cigna used across the organization. Working on Cigna's first mobile applications including working directly on the mobile services platform which was a Python (Django) API to help transform legacy SOAP API's into more modern REST + JSON so they were more easily consumed by mobile devices. Also worked directly on and contributed to the myCigna Android application. I was one of the few engineers on the team that could work on the complete stack from the backend services API, Python API and the Android application}
  \adcvrowskip
  \textbf{Relevant Technologies} Android, Python, REST, JSON, Django, Java, J2EE, Spring Framework, Spring Integration, Spring WS, IBM Websphere, XMLBeans, XSLT, Schema, WSDL, DB2, Oracle DB, CICS transactions, ESB
  
  \adcvrowskip
  {\textbf{Cigna}, Bloomfield, CT}
  
  \adcvrowtwo{\textbf{Senior Application Developer}, EAS} {Jan 2008-2011}
  \adcvrowmulti{Participated in EAS's first major release into production creating and supporting several major key web services that were critical to the business. One of the highlights of this role I was able to design and implemented changes to lower overall response time and lower the amount of MIPS utilized on mainframe systems. Personally responsible for the greatest reduction in MIPS: reduced utilization by 70\% and received a company award for this work.}
  \textbf{Relevant Technologies} Java, J2EE, Spring Framework, ODSI, IBM Websphere, BEA Weblogic, XMLBeans, XQuery, XSLT, SOA, SOAP, Schema, WSDL, DB2, Oracle DB, MS SQL, CICS transactions
  
  \adcvrowskip
  {\textbf{Cigna}, Bloomfield, CT}
  
  \adcvrowtwo{\textbf{Application Developer}, SSO}{Jan 2006-2008}
  \adcvrowmulti{Worked on a team responsible for authorization, authentication and login flows for systems across Cigna. Worked on enhancements, production fixes and other related project work for two large Java applications relating to SSO (Single Sign On).}
  \textbf{Relevant Technologies} Java, J2EE, JSP, DB2 UDB, CICS transactions, LDAP, XML HTTP Services, Apache Struts, Cigna Java Framework, Hibernate ORM, Spring Framework, XMLBeans, IBM Websphere, Unix LDAP

\end{adcvtabletwo}

\section{Education}

\begin{adcvtabletwo}
  \adcvrowtwo{\textbf{B.S. Computer Science}, \hib{}}{2002-2006}
  \begin{itemize}
    \item Minor in Mathematics
    \item GPA 3.406
    \item Upsilon Pi Epsilon Computer Science Honor Society Spring 2006
    \item SHU Football NCAA Division I–AA/FCS 2002-2005
  \end{itemize}
\end{adcvtabletwo}

\section{Personal projects}

\begin{adcvtabletwo}
  \textbf{Suadeo (2020-Present) - }
  Social network application for TV \& movies. Written in react native and Node.js express for the middletier and neo4j for the database. A fun project I worked on with friends during covid to share what we are watching with the people that matter to you most. I focused most of my development on the node.js backend and the graph database with some work on the react native app. I also helped automate our build and deploy process to make ease our development cycles.
  
  https://www.suadeo.io/

  \adcvrowskip
  
  \textbf{Barnyard Fart Fest (2014-2017) - }
  Developed a memory type matching game for all ages. I was able learned a lot about graphics, animations, OpenGL \& build a multi-platform game written in Java.
  
  \adcvrowskip
  
  \textbf{Web Mail Scraper Outlook (2015-2017) - }
  Developed a free application that will screen scraper an OWA 2007 website so you can check your mail natively on your Android device. This was built because many corporate environments don’t allow you to setup your email on your personal phone. This app generated over 100k+ downloads.
  
  \adcvrowskip
  
  \textbf{Binary Clock Wallpaper (2012) - }
  A simple, efficient live wallpaper for android. This was my first published app to the market.
  
  https://play.google.com/store/apps/details?id=com.bazos.wallpaper.binary.lite
  
  \adcvrowskip

  \textbf{Disposable Camera App (2012) - }
  Built for my wedding developed a disposable camera application that allows users to take pictures that instantly get uploaded to my personal website. To prevent bogus photos from people not at the wedding I used geocoding to ensure they were within an appropriate distance of the venue.
\end{adcvtabletwo}

\end{document}
